Comparison of three similarity scores for bullet LEA matching\tnoteref{t1}\tnoteref{t2}

### 2019-12-09 index.Rnw
More explicit citation to aoas paper

In order to evaluate CMS, we must first identify peaks and valleys in each of the signatures, then determine whether these peaks and valleys overlap sufficiently. Features which firearms examiners assess visually depend on the identification of these extrema. If there are at least six consecutive matching striae, the bullets are considered to be similar in practice \citep{biasotti_firearms_1997,nichols_scientific_2006}. CMS in this setting are counted as the number of consecutively matching peaks in signatures of two aligned lands. Peaks -- rather than peaks and valleys -- are used for this determination in part because it is difficult to visually assess valleys except as relative to peaks. Utilizing automatic alignment based on maximum cross correlation (as opposed to matching striation marks) allows the possibility that two lands will have zero consecutive matching striae; this would not occur with manual alignment based on striation marks, as the examiner typically lines up two distinctive markings, resulting in at least one matching striation mark.

@@

\autoref{fig:h44} shows an overview of all scores from pairs of questioned bullets with all other bullets. On the left of \autoref{fig:h44} there are ten strips labelled 1 through 10. These strips correspond to known barrels 1 through 10. Each barrel was test-fired twice, so each of the questioned bullets (shown along the $y$ axis) matches two bullets fired from a known barrel. Colored tiles are used to show the strength of the comparison; light grey colors correspond to low similarity scores, dark colors correspond to high similarity scores. Ground truth is encoded in this figure as a thin, dark, colored frame for all pairs of same-source bullets. 
Ideally, we want to see one barrel with two dark-filled, dark-framed tiles for each questioned bullet, and light grey tiles for all other barrels, indicating a match between a questioned bullet and a single barrel. This expectation is met for all questioned bullets, i.e.\ the automatic matching  identifies the correct barrel for all questioned bullets. For two of the questioned bullets, 'I' and 'F', the similarity scores to the matching barrels are considerably smaller than for the other questioned bullets.

@@

\section{Evaluating the Random Forest Algorithm}
The random forest SAM scores correctly separate known matches from known non-matches, using SAM scores to aggregate land-to-land scores into a bullet-to-bullet comparison. With no errors at the bullet-to-bullet level, we can now evaluate the scores in light of (R1) and (R2). In this section, we will compare the random forest scores to cross correlation scores; cross correlation is one of the components of the random forest, but has also been used to quantify the strength of a match in its own right \citep{chuPilotStudyAutomated2010}. In addition, both scoring methods use the same scale (0 to 1) and are continuous along that interval; other evaluation methods, such as consecutive matching striae, are discrete and more difficult to directly compare to continuous measurements.

>>>>

In order to evaluate CMS, we must first identify peaks and valleys in each of the signatures, then determine whether these peaks and valleys overlap sufficiently. Features which firearms examiners assess visually depend on the identification of these extrema. If there are at least six consecutive matching striae, the bullets are considered to be similar in practice \citep{biasotti_firearms_1997,nichols_scientific_2006}. CMS in this setting are counted as the number of consecutively matching peaks in signatures of two aligned lands. Peaks -- rather than peaks and valleys -- are used for this determination in part because it is difficult to visually assess valleys except as relative to peaks. Utilizing automatic alignment based on maximum cross correlation (as opposed to matching striation marks) allows the possibility that two lands will have zero consecutive matching striae; this would not occur with manual alignment based on striation marks, as the examiner typically lines up two distinctive markings, resulting in at least one matching striation mark. The algorithms used to identify peaks and valleys in each signature and determine CMS from the peak and valley identifications are described in more detail in \citep[p. 2340, step 3 -- 4]{aoas2}.

@@

\autoref{fig:h44} shows an overview of all scores from pairs of questioned bullets with all other bullets. On the left of \autoref{fig:h44} there are ten strips labelled 1 through 10. These strips correspond to known barrels 1 through 10. Each barrel was test-fired twice, so each of the questioned bullets (shown along the $y$ axis) matches two bullets fired from a known barrel. Colored tiles are used to show the similarity score: light grey colors correspond to low similarity scores, dark colors correspond to high similarity scores. Ground truth is encoded in this figure as a thin, dark, colored frame for all pairs of same-source bullets. 
Ideally, we want to see one barrel with two dark-filled, dark-framed tiles for each questioned bullet, and light grey tiles for all other barrels, indicating a match between a questioned bullet and a single barrel. This expectation is met for all questioned bullets, i.e.\ the automatic matching  identifies the correct barrel for all questioned bullets. For two of the questioned bullets, 'I' and 'F', the similarity scores to the matching barrels are considerably smaller than for the other questioned bullets.

@@

\section{Evaluating the Random Forest Algorithm}
The random forest SAM scores correctly separate known matches from known non-matches, using SAM scores to aggregate land-to-land scores into a bullet-to-bullet comparison. With no errors at the bullet-to-bullet level, we can now evaluate the scores in light of (R1) and (R2). In this section, we will compare the random forest scores to cross correlation scores; cross correlation is one of the components of the random forest, but has also been used to quantify the similarity of two signatures in its own right \citep{chuPilotStudyAutomated2010}. In addition, both scoring methods use the same scale (0 to 1) and are continuous along that interval; other evaluation methods, such as consecutive matching striae, are discrete and more difficult to directly compare to continuous measurements.
